---
title: "Adolescent MDD & Brain: Main Results"
author: "X Shen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    code_folding: hide
---

* * *
## Contact 

X Shen (xueyi.shen@ed.ac.uk)

* * *
## R settings

Required packages: 
 
 - dplyr
 - readr
 - ggplot2

Extra packages for Rmarkdown:

 - rmarkdown
 - knitr

Required inputs:
 - result objects from scripts in the ANALY folder

ABCD data: [release 2.0.1](https://nda.nih.gov/data_dictionary.html?source=ABCD%2BRelease%2B2.0&submission=ALL)
 
* * *
## Results

Model: Brain measures ~ MDD/Depressive symptoms (by child/caregiver)

```{r message=FALSE}
library(dplyr)
library(rmarkdown)
library(data.table)
library(knitr)
library(kableExtra)
library(ggplot2)

load('../../result/i.Main_result/YouthDepre_brain_reorganised_forweb.RData')
result=obj.disply
```

### CBCL.dsm5.depre.caregiver{.tabset}
#### Cortical thickness
```{r}
dat.IM=result$V3
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V3 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical surface area
```{r}
dat.IM=result$V8
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V8 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical sulcal depth
```{r}
dat.IM=result$V13
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V13 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical volume
```{r}
dat.IM=result$V18
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V18 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter fractional anisotropy
```{r}
dat.IM=result$V23
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V23 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter mean diffusivity
```{r}
dat.IM=result$V28
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V28 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

### Depressive symptoms.caregiver{.tabset}
#### Cortical thickness
```{r}
dat.IM=result$V2
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V2 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical surface area
```{r}
dat.IM=result$V7
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V7 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical sulcal depth
```{r}
dat.IM=result$V12
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V12 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical volume
```{r}
dat.IM=result$V17
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V17 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter fractional anisotropy
```{r}
dat.IM=result$V22
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V22 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter mean diffusivity
```{r}
dat.IM=result$V27
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V27 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

### Depressive symptoms.child{.tabset}
#### Cortical thickness
```{r}
dat.IM=result$V5
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V5 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical surface area
```{r}
dat.IM=result$V10
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V10 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical sulcal depth
```{r}
dat.IM=result$V15
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V15 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical volume
```{r}
dat.IM=result$V20
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V20 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter fractional anisotropy
```{r}
dat.IM=result$V25
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V25 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter mean diffusivity
```{r}
dat.IM=result$V30
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V30 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

### MDD.caregiver{.tabset}
#### Cortical thickness
```{r}
dat.IM=result$V1
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V1 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical surface area
```{r}
dat.IM=result$V6
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V6 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical sulcal depth
```{r}
dat.IM=result$V11
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V11 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical volume
```{r}
dat.IM=result$V16
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V16 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter fractional anisotropy
```{r}
dat.IM=result$V21
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V21 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter mean diffusivity
```{r}
dat.IM=result$V26
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V26 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

### MDD.child{.tabset}
#### Cortical thickness
```{r}
dat.IM=result$V4
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V4 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical surface area
```{r}
dat.IM=result$V9
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V9 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical sulcal depth
```{r}
dat.IM=result$V14
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V14 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### Cortical volume
```{r}
dat.IM=result$V19
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V19 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter fractional anisotropy
```{r}
dat.IM=result$V24
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V24 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

#### White matter mean diffusivity
```{r}
dat.IM=result$V29
```

```{r, message=FALSE, fig.height=nrow(dat.IM)*0.2, fig.width=9, fig.pos="H"}

dat.IM[,2:(ncol(dat.IM)-1)]=apply(dat.IM[,2:(ncol(dat.IM)-1)],MARGIN = 2,as.numeric)
dat.IM$`p corr`=gsub('\\*','',dat.IM$`p corr`) %>% as.numeric
dat.IM=dat.IM[order(dat.IM$Beta),]
dat.IM$ord=1:nrow(dat.IM)
dat.IM$sig = 'pcor>=0.05'
dat.IM$sig[dat.IM$`p corr`<0.05]='pcor<0.05'
dat.IM$sig = as.factor(dat.IM$sig)
ggplot(dat.IM, aes(x=reorder(`Dependent variable`,ord), y=Beta)) + 
  geom_point(aes(colour = sig),  position=position_dodge(width = 0.1), stat="identity", size=3) +
  geom_errorbar(aes(ymin=Beta-std, ymax=Beta+std), width=.1,
                position=position_dodge(.9),colour="grey")+
  theme(
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.line.x = element_line(size=0.5),
    axis.text=element_text(size=10), axis.title=element_text(size=11),
    plot.title = element_text(lineheight=1, face="bold", vjust=1, hjust=0.5,size=9),
    strip.text = element_text(size=8),
    plot.margin=unit(c(1,1,1,3),'mm')) +
  ylab("Standardised regression coefficient") + xlab('Phenotype')+
  scale_x_discrete(position='top')+
  geom_hline(yintercept=0,color = "black", size=0.3)+
  coord_flip()

```


```{r, message=FALSE}

result$V29 %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

